---
title: "Analysis in R"
author: "Barry Siu"
date: 2026-09-23
---
## Running Analysis in R

```{r}
#| message: false
#| warning: false
library(tidyverse)
library(ggplot2)
library(palmerpenguins)
```

```{r}
head(penguins)
```

```{r}
#| fig-cap: "Figure 1: Body mass of penguins by species."
penguin_data <- penguins
penguin_data |> 
    group_by(species) |> 
    summarise(
    mean_mass = mean(body_mass_g, na.rm = TRUE)) |> 
    ggplot(aes(x = species, y = mean_mass)) +
    geom_col()
```

```{r}
#| message: false
#| warning: false
#| fig-cap: " Figure 2: Body mass compared to flipper length of penguins"
ggplot(penguins, aes(x = flipper_length_mm, 
                     y = body_mass_g, 
                     color = species)) +
  geom_point()
```

## Conclusions

I loaded in the palmerpenguins dataset and first displayed the data frame as a tibble. Afterwards I plotted the mean mass of each species of penguins, which showed that Gentoo had the highest mean mass. For my last analysis I plotted body mass and flipper length on a scatter plot, which showed that Gentoo also had both the largest flipper length and body mass.